\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-12 docs/paper.tex
Introduction, ethics

\section{Introduction}
TODO
- Introduction to the problem
- Enumeration of sections this paper talks about

Domain names were originally designed to support only ASCII characters.
The proposal of Internationalized Domain Name IDN) benefits non-English speaking people, however, it also presents the potential vulnerability.

In this paper, we would analyze XXX top level .com domain by means of clustering possible homograph domains and classifying the owner of them.
In section 2, we talked about the background and history of Internationalized Domain Name (IDN) and the vulnerability behind it.
In section 3, several relevant researches are briefly introduced, which provide a couple of possible solutions to address IDN homograph attack.
We will also present the IDN policies of current major browsers in this section.
Section 4 describes the methodology of data collection and analysis we adopt in this project.
In the next section, we comment on different analysis results and explain the consequences of caveats.
For the last section, we briefly explain the ethical considerations of the research.

\section{Background}
TODO
- DNS: explanation
- IDN: history, explanation
- Browsers: display of IDNs, algorithms

Domain name system contains the relationship between domain names with Internet Protocol(IP) address.
It can can translate domain names to Internet Protocol(IP) address.
At beginning, domain names support only ASCII characters.
In 1996, Internationalized Domain Name (IDN) was proposed by Martin Drst for the purpose of letting non-English speaking people use Internet without additional restrictions.
This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential vulnerability.
For example, Cyrillic letter ’a’ can look identical to Latin letter ’a’ depending on the font.
In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
Malicious attackers can then register a domain where one of the letters is actually Cyrillic but whose representation matches a Latin one.
Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.

Currently, most popular website will show the hostname in Unicode depends on the language setting to defend IDN attack.
For example, Chrome will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language.

@@

\subsection{Manual Classification}
The last part of the data processing was the classification of the homograph domain names.
This classification was done manually, to be able to differentiate between scam and unrelated websites.
Some domains expired at the time of the classification, and were subsequently deleted from the output file.

@@

\begin{table*}[!ht]
\centering
\begin{tabular}{llr}
\hline
Registrant organization              & Registrant email           & \# of homograph IDNs \\ \hline
Domains By Proxy, LLC                & --                         & 89                   \\
Super Privacy Service c/o Dynadot    & privacy@dynadot.com        & 23                   \\
Domain Registries Foundation         & --                         & 22                   \\
Duong Thien                          & thiendv@outlook.com        & 18                   \\
Syngenuity Limited                   & manager@syngenuity.com     & 12                   \\
Helpnet: Brand Development \& Sales  & help@strongestbrands.com   & 12                   \\
ONUNO L.L.C.                         & corucas@gmail.com          & 11                   \\
Privacy Protection Service INC d/b/a & contact@privacyprotect.org & 10                   \\
Hubertus Henz                        & hu\_h5@yahoo.de            & 9                    \\
wuyu                                 & wy65535@126.com            & 7                    \\ \hline
\end{tabular}
\caption{Top ten registrants with the most homograph IDNs.}
\label{top-registrants-homograph-idns}
\end{table*}

\section{Ethical Considerations}
TODO
- Publicly available information
- Delay between whois to not saturate server, also only in small subset (about 1k domains)
- Brief explanation why this research is ethical

>>>>

\section{Introduction}
Domain names were originally designed to only support ASCII characters.
Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst for the purpose of letting non-English speaking people use Internet without additional restrictions.
This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential vulnerability.
For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
Malicious attackers can then register a domain where one of the letters is actually Cyrillic but whose representation matches a Latin one.
Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.

In this paper, we analyze the impact of this attack.
Section 2 explains past and present policies of major browsers and top level domain registrants in an attempt to prevent the attack.
Section 3 explores relevant work in the literature related to homograph attacks.
Section 4 describes the methodology of data collection and analysis adopted in this project.
Section 5 comments the different results obtained.
Section 6 addresses the ethical concerns regarding the data collection.
Section 7 presents the conclusions obtained from this project.

\section{Background}
TODO
- Browsers policy
- TLDs policy

@@

\subsection{Manual Classification}
The last part of the data processing was the classification of the homograph domain names.
This classification was done manually, to be able to differentiate between scam and unrelated websites.
To help with the classification and speed up the process, we queried the \textit{WHOIS} records~\footnote{\url{https://whois.icann.org}} of every homograph domain name.
Some domains expired at the time of the classification, and were subsequently deleted from the output file.

@@

\begin{table*}[ht!]
\centering
\begin{tabular}{llr}
\hline
Registrant organization              & Registrant email           & \# of homograph IDNs \\ \hline
Domains By Proxy, LLC                & --                         & 89                   \\
Super Privacy Service c/o Dynadot    & privacy@dynadot.com        & 23                   \\
Domain Registries Foundation         & --                         & 22                   \\
Duong Thien                          & thiendv@outlook.com        & 18                   \\
Syngenuity Limited                   & manager@syngenuity.com     & 12                   \\
Helpnet: Brand Development \& Sales  & help@strongestbrands.com   & 12                   \\
ONUNO L.L.C.                         & corucas@gmail.com          & 11                   \\
Privacy Protection Service INC d/b/a & contact@privacyprotect.org & 10                   \\
Hubertus Henz                        & hu\_h5@yahoo.de            & 9                    \\
wuyu                                 & wy65535@126.com            & 7                    \\ \hline
\end{tabular}
\caption{Top ten registrants with the most homograph IDNs.}
\label{top-registrants-homograph-idns}
\end{table*}

\section{Ethical Considerations}
The domain information used in this project is publicly available and was voluntarily provided by the registrants of the domains.
The full \texttt{.com} domain zone snapshot won't be publicly disclosed, as its access requires a paid subscription.
The retrieval of the \textit{WHOIS} information was performed only for the homograph internationalized domain names, which were about one thousand.
It was done with a significant delay between petitions (3 seconds) in order to avoid saturating the server.
